Red Wine Exploration by Sam Chen
========================================================

> **Overview**: This data set contains 1,599 red wines with 11 variables on the chemical properties of the wine. At least 3 wine experts rated the quality of each wine, providing a rating between 0 (very bad) and 10 (very excellent).

> **Key question**: "What chemical properties are most important in terms of predicting the quality of wine?"

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis.
# install.packages("ggplot2", dependencies = T) 
# install.packages("knitr", dependencies = T)
# install.packages("dplyr", dependencies = T)

library(ggplot2)
library(knitr)
library(dplyr)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Load_the_Data}
# Load the Data
rw <- read.csv('wineQualityReds.csv')
```

# Univariate Plots Section

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots}
# show the diemnsion of the dataset
dim(rw)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# shoe the structure of the dataset
str(rw)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Show the summary statistics of the dataset
summary(rw)
```

Our data consists of 13 variables, with almost 1,600 observations.
There are 11 variables on the chemical properties of the wine.

As the key question is to understand which chemical properties are the most important of predicing the quality of red wine, I would like to first look at all the distribution plots for all the 11 chemical properties to see if there's anything catching my eye.

```{r echo=FALSE, message=FALSE, warning=FALSE}
names(rw)
```

First, let's take a look for the distribution of quality.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore quality
ggplot(aes(quality), data = rw) +
  geom_histogram()
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore quality
summary(rw$quality)
```
All the red wine quality ratings are range from 3 - 8. 
There's no any wine that was rated super bad(0-2) or super awesome(9-10).
Moreover, most of the wines are rated between 5-6.
The mean of the quality ratings is 5.636 and the median of the quality ratings is 6.000.

Now's take a closer look at the 11 chemical properties within the data set.

1. fixed.acidity(original)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore fixed.acidity
# qplot -- qplot(fixed.acidity, data = rw)
ggplot(aes(fixed.acidity), data = rw) +
  geom_histogram()
```

The histogram of fixed.acidity shows that fixed.acidity is slightly skewed to the right.
Let's see the log plot.

1. fixed.acidity(log)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore fixed.acidity
# qplot -- qplot(fixed.acidity, data = rw)
ggplot(aes(fixed.acidity), data = rw) +
  geom_histogram() + 
  scale_x_log10(breaks=4:16)
```

The Log plot is much closer to the bell curve of a normal distribution.
Let's see the summary:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore fixed.acidity
summary(rw$fixed.acidity)
```
The mean for fixed.acidity is 8.32 and the median is 7.90. 
Most of the red wines have the fixed.acidity between 7.10 to 9.20. 

2. volatile.acidity

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore volatile.acidity
ggplot(aes(volatile.acidity), data = rw) +
  geom_histogram()
```

The histogram of volatile.acidity shows that volatile.acidity is slightly right-skewed. 
Let's the summary of volatile.acidity:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore volatile.acidity
summary(rw$volatile.acidity)
```
Most of the red wines have the volatile.acidity from about 0.40 to o.65.

3. citric.acid

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore citric.acid
ggplot(aes(citric.acid), data = rw) +
  geom_histogram()
```

The histogram of citric.acidity shows that most of the data has citric.acid = 0. This may need future exploration.
Let's see the summary for citric.acidity.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore citric.acid -- summary
summary(rw$citric.acid)
```

The smallest value for citric.acid is 0.000 and the largest value for citric.acid is 1.000. However, 75% of the values are below 0.420. 
Let's see the square root distribution.

3. citric.acid(sqrt)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore citric.acid -- sqrt
ggplot(aes(citric.acid), data = rw) +
  geom_histogram() + 
  scale_x_sqrt()
```

Since in the first plot, 0 is the value that has the largest count, after taking the square root, most of the values are still 0.
As most of the data are between 0 and 1, after taking the square root, they will become bigger value. As a result, there is a blank spot in the plot.
I wonder how citric.acid is connected to quality, and I wonder if the citric.acid values are specific to certain alcoholic levels.

4. residual.sugar

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore residual.sugar
ggplot(aes(residual.sugar), data = rw) +
  geom_histogram()
```

From the histogram of residual.sugar, we can see that it's very long-tailed. Let's see the log plot.

4. residual.sugar(log)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore residual.sugar
ggplot(aes(residual.sugar), data = rw) +
  geom_histogram() + 
  scale_x_log10()
```

We can see from the log plot that the distribution for residual.sugar is more close to normal distribution.
Let's see the summary ofresidual.sugar:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore residual.sugar
summary(rw$residual.sugar)
```

Most red wines have residual.sugar values between 1.9 to 2.6.

5. chlorides

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore chlorides
ggplot(aes(chlorides), data = rw) +
  geom_histogram()
```

From the histogram of chlorides, we can see that it's very long-tailed. Let's see the log plot.

5. chlorides(log)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore chlorides
ggplot(aes(chlorides), data = rw) +
  geom_histogram() + 
  scale_x_log10()
```

The Log plot is much closer to the bell curve of a normal distribution.
Let's see the summary for chlorides:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore chlorides
summary(rw$chlorides)
```

Most of the red wines have chlorides range between 0.07 to 0.09. 
75% of the red wines have chlorides below 0.09.

6. free.sulfur.dioxide

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore free.sulfur.dioxide
ggplot(aes(free.sulfur.dioxide), data = rw) +
  geom_histogram()
```

The histogram of free,sulfur.dioxide is right-skewed. Let's see the log plot.

6. free.sulfur.dioxide(log)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore free.sulfur.dioxide -- log10
ggplot(aes(free.sulfur.dioxide), data = rw) +
  geom_histogram() +
  scale_x_log10()
```

Let's see the summary for free.sulfur.dioxide:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore free.sulfur.dioxide
summary(rw$free.sulfur.dioxide)
```

The largest value for the free.sulfur.dioxide in a red wine is 72.00 which is far away from the 3rd Quantile(21.00) and median(14.00).

7. total.sulfur.dioxide

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore total.sulfur.dioxide
ggplot(aes(total.sulfur.dioxide), data = rw) +
  geom_histogram()
```

The histogram of total.sulfur.dioxide is long-tailed. Let's see the log plot.

7. total.sulfur.dioxide(log)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore free.sulfur.dioxide -- log
ggplot(aes(total.sulfur.dioxide), data = rw) +
  geom_histogram() +
  scale_x_log10()
```

The log plot for total.sulfur.dioxide is close to the bell surve. 
Let's see the summary of total.sulfur.dioxide:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore free.sulfur.dioxide
summary(rw$total.sulfur.dioxide)
```

For the distribution of total.sulfur.dioxide, the mean value is 46.47, and the median value is 38.00. 
75% of the total.sulfur.dioxide value is below 62.00 while the max value is 289.00.

8. density

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore density
ggplot(aes(density), data = rw) +
  geom_histogram()
```

The distribution for density shown in this histogram is close to the pattern for normal distribution.
Let's see the summary of density:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore density
summary(rw$density)
```
Combine the results of the histogram and summary, we can see the density is close to normal distribution, range from 0.9901 to 1.0037.
The median(0.9968) and mean(0.9967) is almost the same!

9. pH

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore pH
ggplot(aes(pH), data = rw) +
  geom_histogram()
```

The pattern for pH's histogram is close to normal distribution.
Let's summary of pH:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore pH
summary(rw$pH)
```

The max value of pH is 4.010 which indicates that all the red wines are acid(pH<7).
Combine the results of the histogram and summary, we can see the pH is close to normal distribution, range from 2.740 to 4.010.
The median(3.3310) and mean(3.311) is almost the same!

10. sulphates

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore sulphates
ggplot(aes(sulphates), data = rw) +
  geom_histogram()
```

It seems that the distribution for sulphates is right-skewed. Let's see the log plot.

10. sulphates(log)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore sulphates -- log
ggplot(aes(sulphates), data = rw) +
  geom_histogram() +
  scale_x_log10()
```

The log plot for sulphates is more close to the bell curve.
Let's see the summary of sulphates:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore sulphates
summary(rw$sulphates)
```

Most of the red wines have the value of sulphates between 0.55 to 0.73 while the Max value is 2.00.

11. alcohol

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore alcohol
ggplot(aes(alcohol), data = rw) +
  geom_histogram()
```

The distribution for the alcohol shown in this histogram is right-skewed. Let's see the log plot.

11. alcohol(log)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore alcohol -- log
ggplot(aes(alcohol), data = rw) +
  geom_histogram() +
  scale_x_log10()
```

Let's see the summary for alcohol:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore alcohol
summary(rw$alcohol)
```
The alcohol values for the red wines are range from 8.40 to 14.90. 
I wonder if the alcohol effects the quality.

# Univariate Analysis

### What is the structure of your dataset?
There are 1,599 red wines in the data with 11 chemical properties(fixed.acidity, volatile.acidity, citric.acid, residual.sugar, chlorides, free.sulfur.dioxide, total.sulfur.dioxide, density, pH, sulphates, alcohol). 

##### Other Observations:
* Most of the wines are rated from 5-6.
* Chemical Properties that is right-skewed: fixed.acidity, citric.acid, residual.sugar, chlorides, free.sulfur.dioxide, total.sulfur.dioxide, sulphates, alcohol.
* Most of the red wines have the volatile.acidity from about 0.40 to o.65.
* Residual.sugar and Chlorides are heavily long-tailed. 
* Chemical Properties that is close to normal distribution: pH, density
* Most of the red wines have chlorides range between 0.07 to 0.09. 
* Most red wines have residual.sugar values between 1.9 to 2.6.
* 75% of the red wines have chlorides below 0.09, while the max value is 0.61.
* The max value of pH is 4.010 which indicates that all the red wines are acid(pH<7).
* Most of the red wines have the value of sulphates between 0.55 to 0.73 while the Max value is 2.00.
* The alcohol values for the red wines are range from 8.40 to 14.90. 

### What is/are the main feature(s) of interest in your dataset?

The main features in the data set are quality and alcohol. I’d like to determine which features are best for predicting the quality for red wine. I suspect volatile.acidity and some combination of the other variables can be used to build a predictive model to red wine quality.

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

volatile.acidity, residual.sugar, chlorides, density, sulphates and alcohol likely contribute to the quality of red wine. I think volatile.acidity and alcohol probably contribute most of the quality after researching information on red wines quality.

### Did you create any new variables from existing variables in the dataset?
Not at the moment.

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?
I log-transformed the right skewed price and volume distributions.(fixed-acidity, residual.sugar, chlorides, free.sulfur.dioxide, total.sulfur.dioxide, sulphates, alcohol) 

# Bivariate Plots Section

> **Tip**: Based on what you saw in the univariate plots, what relationships
between variables might be interesting to look at in this section? Don't limit
yourself to relationships between a main output feature and one of the
supporting variables. Try to look at relationships between supporting variables
as well. I think residual.sugar and pH probably contribute most of the quality after researching information on red wines quality.

```{r echo=FALSE, Bivariate_Plots}
round(cor(rw), 3)
```

```{r echo=FALSE, Bivariate_Plots}
# install.packages('GGally')
# install.packages('scales')
# install.packages('memisc')
# install.packages("knitr")
# install.packages("dplyr")
# library('ggplot2')
# library('GGally')
# library('scales')
# library('memisc')
# library('knitr')
# library('dplyr')

set.seed(20022012)
rw_samp <- rw[sample(1:length(rw$quality), 1000),]
ggpairs(rw_samp, wrap = c(shape = I('.'), outlier.shape = I('.')))
```

From a subset of the data, sulphates, citric.acid, total.sulfur.dioxide do not seem to have strong correlations with quality, but density is moderately correlated with alcohol. I want to look closer at scatter plots involving quality and some other variables like alcohol, volatile.acidity, and density.

Let's see the scatter plot for quality and alcohol:

```{r echo=FALSE, Bivariate_Plots}
ggplot(aes(x = alcohol, y= quality), data = rw) + 
    geom_point()
```

Seems that we can not clearly see the pattern from the plot.
Let's transfrom the data and try to add some jitter:

```{r echo=FALSE, Bivariate_Plots}
ggplot(aes(x = alcohol, y= quality), data = rw) + 
    geom_jitter(alpha= 1/2) +
    scale_x_log10(breaks=8:15) +
    ylim(2,8)
```

From the plot, we can see that the distribution in the scatter plot slightly shifts from the left-bottom corner to the top-right, this indicates that red wines' quality is correlated to the alcohol values in the data. Most red wines in the data have alcohol percantage between 9 to 12. 

```{r echo=FALSE, Bivariate_Plots}
alcohol_lm = lm(formula = quality ~ alcohol, data = subset(rw, alcohol <= 
    quantile(rw$alcohol, 0.999)))
```

```{r echo=FALSE, Bivariate_Plots}
summary(alcohol_lm)
```

From the summary, we know that based on R^2 value, alcohol explains 23.14% of red wines' quality.

Let's see the scatter plot for quality and volatile.acidity:

```{r echo=FALSE, Bivariate_Plots}
ggplot(aes(x = volatile.acidity, y= quality), data = rw) + 
    geom_point()
```

The data suffers from overplotting, let's add some jitter, alpha and transforming the data using log.

```{r echo=FALSE, Bivariate_Plots}
ggplot(aes(x = volatile.acidity, y= quality), data = rw) + 
    geom_jitter(alpha = 1/3) + 
    scale_x_log10() +
    xlim(0, 2)
```

After applying jitter, alpha and log-transform, we can se the distribution of the data in the plot move from top-left to bottom-right which indicates that quality is negetively correlated with red wine quality. Most red wines have volatile.acidity between 0.25 to 0.75. We can tell that red wines with higher volatile.acidity tend to have lower quality while red wines with lower volatile.acidity tend to have better quality.

```{r echo=FALSE, Bivariate_Plots}
volatile_lm = lm(formula = quality ~ volatile.acidity, data = subset(rw, volatile.acidity <= 
    quantile(rw$volatile.acidity, 0.999)))
```

```{r echo=FALSE, Bivariate_Plots}
summary(volatile_lm)
```
From the summary, we know that based on R^2 value, alcohol only explains 14.74% of red wines' quality.

Finally, let's see the scatter plot between quality and density:

```{r echo=FALSE, Bivariate_Plots}
ggplot(aes(x = density, y= quality), data = rw) + 
    geom_point()
```

The data suffers from overplotting, let's add some jitter, alpha and transforming the data using log.

```{r echo=FALSE, Bivariate_Plots}
ggplot(aes(x = density, y= quality), data = rw) + 
    geom_jitter(alpha = 1/3) + 
    scale_x_log10() +
    xlim(0.99,1)
```

```{r echo=FALSE, Bivariate_Plots}
density_lm = lm(formula = quality ~ density, data = subset(rw, density <= 
    quantile(rw$density, 0.999)))
```

```{r echo=FALSE, Bivariate_Plots}
summary(density_lm)
```

Based on the plot and the summary, we know that comparing density to quality, most red wines have density between 0.9950 to 0.9975. Quality and density is lack of correlation.

Next, I'll look at the scatter plot between other chemical features with red wine quality.
(sulphates, citric.acid, total.sulfur.dioxide, total.sulfur.dioxide)

First, let's see the scatter plot for quality and sulphates:

```{r echo=FALSE, Bivariate_Plots}
ggplot(aes(x = sulphates, y= quality), data = rw) + 
    geom_point()
```

The data suffers from overplotting, let's add some jitter, alpha and transforming the data using log.

```{r echo=FALSE, Bivariate_Plots}
ggplot(aes(x = sulphates, y= quality), data = rw) + 
    geom_jitter(alpha = 1/3) +
    scale_x_log10(breaks=1:10)
```

It seems to be some correlation between quality and sulphates. Let's dive into the summary for linear model to know more.

```{r echo=FALSE, Bivariate_Plots}
sulphates_lm = lm(formula = quality ~ sulphates, data = subset(rw, sulphates <= 
    quantile(rw$sulphates, 0.999)))
```

```{r echo=FALSE, Bivariate_Plots}
summary(sulphates_lm)
```

Based on R^2 value, sulphates only explains 7.651% of red wines' quality!

Now, let's see the scatter plot for quality and citric.acid:
```{r echo=FALSE, Bivariate_Plots}
ggplot(aes(x = citric.acid, y= quality), data = rw) + 
    geom_point()
```

The data suffers from overplotting, let's add some jitter, alpha and transforming the data using log.

```{r echo=FALSE, Bivariate_Plots}
ggplot(aes(x = citric.acid, y= quality), data = rw+1) + 
    geom_jitter(alpha = 1/3) +
    scale_x_log10(breaks=1:2)
```

```{r echo=FALSE, Bivariate_Plots}
citric.acid_lm = lm(formula = quality ~ citric.acid, data = subset(rw, citric.acid <= 
    quantile(rw$citric.acid, 0.999)))
```

```{r echo=FALSE, Bivariate_Plots}
summary(citric.acid_lm)
```

Based on the plot and the summary, the horizontal strips in the plot and the R^2 values indicate that quality and citric.acid is lack of correlation.

Let's see the scatter plot for quality and total.sulfur.dioxide:

```{r echo=FALSE, Bivariate_Plots}
ggplot(aes(x = total.sulfur.dioxide, y= quality), data = rw) + 
    geom_point()
```

The data suffers from overplotting, let's add some jitter, alpha and transforming the data using log.

```{r echo=FALSE, Bivariate_Plots}
ggplot(aes(x = total.sulfur.dioxide, y= quality), data = rw) + 
    geom_jitter(alpha = 1/3) +
    scale_x_log10(breaks=1:10)
```

```{r echo=FALSE, Bivariate_Plots}
total.sulfur.dioxide_lm = lm(formula = quality ~ total.sulfur.dioxide, data = subset(rw, total.sulfur.dioxide <= 
    quantile(rw$total.sulfur.dioxide, 0.999)))
```

```{r echo=FALSE, Bivariate_Plots}
summary(total.sulfur.dioxide_lm)
```

Based on the plot and the summary, the horizontal strips in the plot indicate that quality and total.sulfur.dioxide is lack of correlation.

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

Red wine quality correlates with alcohol(23.14%) and volatile.acidity(14.74%) and slightly with sulphates(7.65%). 

As alcohol increases, the variance in quality increase. In the plot of quality versus alcohol, there are horizontal bands where many red wines take on the same quality value at different alcohol points. Based on the R^2 value, alcohol explains only about 23 percent of the variance in quality. Other features of interest can be incorporated into the model to explain the variance in the quality.

Red wines with higher volatile.acidity tend to have lower quality while red wines with lower volatile.acidity tend to have better quality.

We found that quality is lack of correlation with citric.acid, total.sulfur.dioxide and density.

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?
- fixed.acidity appears to have a strong correlation with citric.acid, this may due to they are both acidity chemical features.
- free.sulfur.dioxide appears to have a strong correlation with total.sulfur.dioxide, this may due to they are both a kind of sulfur.dioxide.
- fixed.acidity appears to have a strong and negative correlation with pH, this lines up with the definition of pH values. 

### What was the strongest relationship you found?
The quality of red wines is positively and strongly correlated with sulphates and slightly correlated with alcohol and volatile.acidity.. 

# Multivariate Plots Section

Let's plot the relationship between quality and alcohol using volatile.acidity in color paramater. 

```{r echo=FALSE, Multivariate_Plots}
ggplot(aes(x = alcohol, y = quality), data = rw) +
  geom_jitter(aes(color=volatile.acidity), alpha = 0.5) +
  geom_abline(intercept = -5)
```

```{r echo=FALSE, Multivariate_Plots}
ggplot(aes(x = alcohol , y = quality), data = rw) +
  geom_jitter(aes(color=volatile.acidity), alpha = 0.5) +
  scale_x_log10() +
  labs(title = 'Quality by alcohol(log10)') +
  geom_abline(slope = 5.5)
```

I noticed that there are a few blank region in the data. This may due to the fact that quality datas are in interger format. The graph present linear relationship between quality and alcohol.

Let's see the plot for alcohol and quality using sulphates in the color parameter.

```{r echo=FALSE, Multivariate_Plots}
ggplot(aes(x = alcohol, y = quality), data = rw) +
  geom_jitter(aes(color= sulphates), alpha = 0.5) +
  geom_abline(intercept = -5)
```

```{r echo=FALSE, Multivariate_Plots}
ggplot(aes(x = alcohol, y = quality), data = rw) +
  geom_jitter(aes(color= sulphates), alpha = 0.5) +
  scale_x_log10() +
  labs(title = 'Quality by alcohol(log10)') +
  geom_abline(slope = 5, intercept = 1)
```

The results from the log transformation shows that the darker points are on the bottom-left while light points are on the top-right.

Let's plot the relationship of quality and volatile.acidity using sulphates in color:

```{r echo=FALSE, Multivariate_Plots}
ggplot(aes(x = volatile.acidity, y = quality), data = rw) +
  geom_jitter(aes(color= sulphates), alpha = 0.5) +
  geom_abline(intercept = 8, slope = -5)
```

```{r echo=FALSE, Multivariate_Plots}
ggplot(aes(x = volatile.acidity, y = quality), data = rw) +
  geom_jitter(aes(color= sulphates), alpha = 0.5) +
  scale_x_log10() +
  labs(title = 'Quality by volatile.acidity(log10)') +
  geom_abline(intercept = 4, slope = -5)
```
From the plot we can see that quality and volatile.acidity are negatively related.

Next, let's feed in the model:

```{r echo=FALSE, Multivariate_Plots}
m1 <- lm(quality ~ alcohol, data= rw)
m2 <- update(m1, ~ . + sulphates)
m3 <- update(m2, ~ . + volatile.acidity)
mtable(m1, m2, m3)
```
From the table, we know that even with nice . The model can only explains 33.6% of quality datas. 

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

- Using color on the plot between quality and alcohol help explains the relationship in between. 
- Using color on the plot between quality and volatile.acidity help explains the relationship in between. 
- There's positive relationship between quality and alcohol datas.
- There's negative relationship between quality and volatile.acisidty

### Were there any interesting or surprising interactions between features?


### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

------

# Final Plots and Summary

> **Tip**: You've done a lot of exploration and have built up an understanding
of the structure of and relationships between the variables in your dataset.
Here, you will select three plots from all of your previous exploration to
present here as a summary of some of your most interesting findings. Make sure
that you have refined your selected plots for good titling, axis labels (with
units), and good aesthetic choices (e.g. color, transparency). After each plot,
make sure you justify why you chose each plot by describing what it shows.

### Plot One
```{r echo=FALSE, Plot_One}

```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}

```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}

```

### Description Three

------

# Reflection

- Country/Region that the red wine is produced.
- Storage condition
> **Tip**: Here's the final step! Reflect on the exploration you performed and
the insights you found. What were some of the struggles that you went through?
What went well? What was surprising? Make sure you include an insight into
future work that could be done with the dataset.

> **Tip**: Don't forget to remove this, and the other **Tip** sections before
saving your final work and knitting the final report!