Red Wine Exploration by Sam Chen
========================================================

> **Overview**: This data set contains 1,599 red wines with 11 variables on the chemical properties of the wine. At least 3 wine experts rated the quality of each wine, providing a rating between 0 (very bad) and 10 (very excellent).

> **Key question**: "What chemical properties are most important in terms of predicting the quality of wine?"

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis.
# install.packages("ggplot2", dependencies = T) 
# install.packages("knitr", dependencies = T)
# install.packages("dplyr", dependencies = T)

library(ggplot2)
library(knitr)
library(dplyr)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Load_the_Data}
# Load the Data
rw <- read.csv('wineQualityReds.csv')
```

# Univariate Plots Section

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots}
# show the diemnsion of the dataset
dim(rw)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# shoe the structure of the dataset
str(rw)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Show the summary statistics of the dataset
summary(rw)
```

Our data consists of 13 variables, with almost 1,600 observations.
There are 11 variables on the chemical properties of the wine.

As the key question is to understand which chemical properties are the most important of predicing the quality of red wine, I would like to first look at all the distribution plots for all the 11 chemical properties to see if there's anything catching my eye.

```{r echo=FALSE, message=FALSE, warning=FALSE}
names(rw)
```

First, let's take a look for the distribution of quality.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore quality
ggplot(aes(quality), data = rw) +
  geom_histogram()
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore quality
summary(rw$quality)
```
All the red wine quality ratings are range from 3 - 8. 
There's no any wine that was rated super bad(0-2) or super awesome(9-10).
Moreover, most of the wines are rated between 5-6.
The mean of the quality ratings is 5.636 and the median of the quality ratings is 6.000.

Now's take a closer look at the 11 chemical properties within the data set.

1. fixed.acidity(original)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore fixed.acidity
# qplot -- qplot(fixed.acidity, data = rw)
ggplot(aes(fixed.acidity), data = rw) +
  geom_histogram()
```

The histogram of fixed.acidity shows that fixed.acidity is slightly skewed to the right.
Let's see the log plot.

1. fixed.acidity(log)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore fixed.acidity
# qplot -- qplot(fixed.acidity, data = rw)
ggplot(aes(fixed.acidity), data = rw) +
  geom_histogram() + 
  scale_x_log10(breaks=4:16)
```

The Log plot is much closer to the bell curve of a normal distribution.
Let's see the summary:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore fixed.acidity
summary(rw$fixed.acidity)
```
The mean for fixed.acidity is 8.32 and the median is 7.90. 
Most of the red wines have the fixed.acidity between 7.10 to 9.20. 

2. volatile.acidity

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore volatile.acidity
ggplot(aes(volatile.acidity), data = rw) +
  geom_histogram()
```

The histogram of volatile.acidity shows that volatile.acidity is slightly right-skewed. 
Let's the summary of volatile.acidity:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore volatile.acidity
summary(rw$volatile.acidity)
```
Most of the red wines have the volatile.acidity from about 0.40 to o.65.

3. citric.acid

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore citric.acid
ggplot(aes(citric.acid), data = rw) +
  geom_histogram()
```

The histogram of citric.acidity shows that most of the data has citric.acid = 0. This may need future exploration.
Let's see the summary for citric.acidity.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore citric.acid -- summary
summary(rw$citric.acid)
```

The smallest value for citric.acid is 0.000 and the largest value for citric.acid is 1.000. However, 75% of the values are below 0.420. 
Let's see the square root distribution.

3. citric.acid(sqrt)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore citric.acid -- sqrt
ggplot(aes(citric.acid), data = rw) +
  geom_histogram() + 
  scale_x_sqrt()
```

Since in the first plot, 0 is the value that has the largest count, after taking the square root, most of the values are still 0.
As most of the data are between 0 and 1, after taking the square root, they will become bigger value. As a result, there is a blank spot in the plot.
I wonder how citric.acid is connected to quality, and I wonder if the citric.acid values are specific to certain alcoholic levels.

4. residual.sugar

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore residual.sugar
ggplot(aes(residual.sugar), data = rw) +
  geom_histogram()
```

From the histogram of residual.sugar, we can see that it's very long-tailed. Let's see the log plot.

4. residual.sugar(log)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore residual.sugar
ggplot(aes(residual.sugar), data = rw) +
  geom_histogram() + 
  scale_x_log10()
```

We can see from the log plot that the distribution for residual.sugar is more close to normal distribution.
Let's see the summary ofresidual.sugar:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore residual.sugar
summary(rw$residual.sugar)
```

Most red wines have residual.sugar values between 1.9 to 2.6.

5. chlorides

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore chlorides
ggplot(aes(chlorides), data = rw) +
  geom_histogram()
```

From the histogram of chlorides, we can see that it's very long-tailed. Let's see the log plot.

5. chlorides(log)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore chlorides
ggplot(aes(chlorides), data = rw) +
  geom_histogram() + 
  scale_x_log10()
```

The Log plot is much closer to the bell curve of a normal distribution.
Let's see the summary for chlorides:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore chlorides
summary(rw$chlorides)
```

Most of the red wines have chlorides range between 0.07 to 0.09. 
75% of the red wines have chlorides below 0.09.

6. free.sulfur.dioxide

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore free.sulfur.dioxide
ggplot(aes(free.sulfur.dioxide), data = rw) +
  geom_histogram()
```

The histogram of free,sulfur.dioxide is right-skewed. Let's see the log plot.

6. free.sulfur.dioxide(log)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore free.sulfur.dioxide -- log10
ggplot(aes(free.sulfur.dioxide), data = rw) +
  geom_histogram() +
  scale_x_log10()
```

Let's see the summary for free.sulfur.dioxide:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore free.sulfur.dioxide
summary(rw$free.sulfur.dioxide)
```

The largest value for the free.sulfur.dioxide in a red wine is 72.00 which is far away from the 3rd Quantile(21.00) and median(14.00).

7. total.sulfur.dioxide

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore total.sulfur.dioxide
ggplot(aes(total.sulfur.dioxide), data = rw) +
  geom_histogram()
```

The histogram of total.sulfur.dioxide is long-tailed. Let's see the log plot.

7. total.sulfur.dioxide(log)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore free.sulfur.dioxide -- log
ggplot(aes(total.sulfur.dioxide), data = rw) +
  geom_histogram() +
  scale_x_log10()
```

The log plot for total.sulfur.dioxide is close to the bell surve. 
Let's see the summary of total.sulfur.dioxide:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore free.sulfur.dioxide
summary(rw$total.sulfur.dioxide)
```

For the distribution of total.sulfur.dioxide, the mean value is 46.47, and the median value is 38.00. 
75% of the total.sulfur.dioxide value is below 62.00 while the max value is 289.00.

8. density

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore density
ggplot(aes(density), data = rw) +
  geom_histogram()
```

The distribution for density shown in this histogram is close to the pattern for normal distribution.
Let's see the summary of density:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore density
summary(rw$density)
```
Combine the results of the histogram and summary, we can see the density is close to normal distribution, range from 0.9901 to 1.0037.
The median(0.9968) and mean(0.9967) is almost the same!

9. pH

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore pH
ggplot(aes(pH), data = rw) +
  geom_histogram()
```

The pattern for pH's histogram is close to normal distribution.
Let's summary of pH:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore pH
summary(rw$pH)
```

The max value of pH is 4.010 which indicates that all the red wines are acid(pH<7).
Combine the results of the histogram and summary, we can see the pH is close to normal distribution, range from 2.740 to 4.010.
The median(3.3310) and mean(3.311) is almost the same!

10. sulphates

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore sulphates
ggplot(aes(sulphates), data = rw) +
  geom_histogram()
```

It seems that the distribution for sulphates is right-skewed. Let's see the log plot.

10. sulphates(log)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore sulphates -- log
ggplot(aes(sulphates), data = rw) +
  geom_histogram() +
  scale_x_log10()
```

The log plot for sulphates is more close to the bell curve.
Let's see the summary of sulphates:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore sulphates
summary(rw$sulphates)
```

Most of the red wines have the value of sulphates between 0.55 to 0.73 while the Max value is 2.00.

11. alcohol

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore alcohol
ggplot(aes(alcohol), data = rw) +
  geom_histogram()
```

The distribution for the alcohol shown in this histogram is right-skewed. Let's see the log plot.

11. alcohol(log)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore alcohol -- log
ggplot(aes(alcohol), data = rw) +
  geom_histogram() +
  scale_x_log10()
```

Let's see the summary for alcohol:

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore alcohol
summary(rw$alcohol)
```
The alcohol percentage for the red wines are range from 8.40 to 14.90. 
I wonder if the alcohol effects the quality.

# Univariate Analysis

### What is the structure of your dataset?
There are 1,599 red wines in the data with 11 chemical properties(fixed.acidity, volatile.acidity, citric.acid, residual.sugar, chlorides, free.sulfur.dioxide, total.sulfur.dioxide, density, pH, sulphates, alcohol). 

##### Other Observations:
* Most of the wines are rated from 5-6.
* Chemical Properties that is right-skewed: fixed.acidity, citric.acid, residual.sugar, chlorides, free.sulfur.dioxide, total.sulfur.dioxide, sulphates, alcohol.
* Residual.sugar and Chlorides are heavily long-tailed. 
* Chemical Properties that is close to normal distribution: pH, density
* Most of the red wines have the volatile.acidity from about 0.40 to o.65.
* Most of the red wines have chlorides range between 0.07 to 0.09. 
* Most red wines have residual.sugar values between 1.9 to 2.6.
* 75% of the red wines have chlorides below 0.09, while the max value is 0.61.
* The max value of pH is 4.010 which indicates that all the red wines are acid(pH<7).
* Most of the red wines have the value of sulphates between 0.55 to 0.73 while the Max value is 2.00.

### What is/are the main feature(s) of interest in your dataset?

The main features in the data set are quality and alcohol. I’d like to determine which features are best for predicting the quality for red wine. I suspect residual.sugar and some combination of the other variables can be used to build a predictive model to red wine quality.

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

volatile.acidity, residual.sugar, chlorides, density, pH and sulphates likely contribute to the quality of red wine. I think residual.sugar and pH probably contribute most of the quality after researching information on red wines quality.

### Did you create any new variables from existing variables in the dataset?
Not at the moment.

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?
I log-transformed the right skewed price and volume distributions.(fixed-acidity, residual.sugar, chlorides, free.sulfur.dioxide, total.sulfur.dioxide, sulphates, alcohol)

The tranformed distribution for 
citric -- sqrt
price appears bimodal with the price peaking around $800 or so and again around $5000. There’s no diamonds priced at $1500.



# Bivariate Plots Section

> **Tip**: Based on what you saw in the univariate plots, what relationships
between variables might be interesting to look at in this section? Don't limit
yourself to relationships between a main output feature and one of the
supporting variables. Try to look at relationships between supporting variables
as well.

```{r echo=FALSE, Bivariate_Plots}
ggpair()



```

# Bivariate Analysis

> **Tip**: As before, summarize what you found in your bivariate explorations
here. Use the questions below to guide your discussion.

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

### What was the strongest relationship you found?


# Multivariate Plots Section

> **Tip**: Now it's time to put everything together. Based on what you found in
the bivariate plots section, create a few multivariate plots to investigate
more complex interactions between variables. Make sure that the plots that you
create here are justified by the plots you explored in the previous section. If
you plan on creating any mathematical models, this is the section where you
will do that.

```{r echo=FALSE, Multivariate_Plots}

```

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

### Were there any interesting or surprising interactions between features?

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

------

# Final Plots and Summary

> **Tip**: You've done a lot of exploration and have built up an understanding
of the structure of and relationships between the variables in your dataset.
Here, you will select three plots from all of your previous exploration to
present here as a summary of some of your most interesting findings. Make sure
that you have refined your selected plots for good titling, axis labels (with
units), and good aesthetic choices (e.g. color, transparency). After each plot,
make sure you justify why you chose each plot by describing what it shows.

### Plot One
```{r echo=FALSE, Plot_One}

```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}

```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}

```

### Description Three

------

# Reflection

- Country/Region that the red wine is produced.
- Storage condition
> **Tip**: Here's the final step! Reflect on the exploration you performed and
the insights you found. What were some of the struggles that you went through?
What went well? What was surprising? Make sure you include an insight into
future work that could be done with the dataset.

> **Tip**: Don't forget to remove this, and the other **Tip** sections before
saving your final work and knitting the final report!