Red Wine Exploration by Sam Chen
========================================================

> **Overview**: This data set contains 1,599 red wines with 11 variables on the chemical properties of the wine. At least 3 wine experts rated the quality of each wine, providing a rating between 0 (very bad) and 10 (very excellent).

> **Key question**: "Which chemical properties influence the quality of red wines?"

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis.
# install.packages("ggplot2", dependencies = T) 
# install.packages("knitr", dependencies = T)
# install.packages("dplyr", dependencies = T)

library(ggplot2)
library(knitr)
library(dplyr)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Load_the_Data}
# Load the Data
rw <- read.csv('wineQualityReds.csv')
```

# Univariate Plots Section

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots}
# show the diemnsion of the dataset
dim(rw)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# shoe the structure of the dataset
str(rw)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Show the summary statistics of the dataset
summary(rw)
```

Our data consists of 13 variables, with almost 1,600 observations.

As the key question is to understand which chemical properties influence the quality of red wine, I would like to first look at all the distribution plots for every chemical properties to see if there's anything catching my eye.

```{r echo=FALSE, message=FALSE, warning=FALSE}
names(rw)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore fixed.acidity
# qplot -- qplot(fixed.acidity, data = rw)
ggplot(aes(fixed.acidity), data = rw) +
  geom_histogram()
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore volatile.acidity
ggplot(aes(volatile.acidity), data = rw) +
  geom_histogram()
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore citric.acid
ggplot(aes(citric.acid), data = rw) +
  geom_histogram()
```
        
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore residual.sugar
ggplot(aes(residual.sugar), data = rw) +
  geom_histogram()
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore chlorides
ggplot(aes(chlorides), data = rw) +
  geom_histogram()
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore free.sulfur.dioxide
ggplot(aes(free.sulfur.dioxide), data = rw) +
  geom_histogram()
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore total.sulfur.dioxide
ggplot(aes(total.sulfur.dioxide), data = rw) +
  geom_histogram()
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore density
ggplot(aes(density), data = rw) +
  geom_histogram()
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore pH
ggplot(aes(pH), data = rw) +
  geom_histogram()
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore sulphates
ggplot(aes(sulphates), data = rw) +
  geom_histogram()
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore alcohol
ggplot(aes(alcohol), data = rw) +
  geom_histogram()
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Explore quality
ggplot(aes(quality), data = rw) +
  geom_histogram()
```

# Univariate Analysis

> **Tip**: Now that you've completed your univariate explorations, it's time to
reflect on and summarize what you've found. Use the questions below to help you
gather your observations and add your own if you have other thoughts!

### What is the structure of your dataset?

### What is/are the main feature(s) of interest in your dataset?

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

### Did you create any new variables from existing variables in the dataset?

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?


# Bivariate Plots Section

> **Tip**: Based on what you saw in the univariate plots, what relationships
between variables might be interesting to look at in this section? Don't limit
yourself to relationships between a main output feature and one of the
supporting variables. Try to look at relationships between supporting variables
as well.

```{r echo=FALSE, Bivariate_Plots}



```

# Bivariate Analysis

> **Tip**: As before, summarize what you found in your bivariate explorations
here. Use the questions below to guide your discussion.

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

### What was the strongest relationship you found?


# Multivariate Plots Section

> **Tip**: Now it's time to put everything together. Based on what you found in
the bivariate plots section, create a few multivariate plots to investigate
more complex interactions between variables. Make sure that the plots that you
create here are justified by the plots you explored in the previous section. If
you plan on creating any mathematical models, this is the section where you
will do that.

```{r echo=FALSE, Multivariate_Plots}

```

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

### Were there any interesting or surprising interactions between features?

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

------

# Final Plots and Summary

> **Tip**: You've done a lot of exploration and have built up an understanding
of the structure of and relationships between the variables in your dataset.
Here, you will select three plots from all of your previous exploration to
present here as a summary of some of your most interesting findings. Make sure
that you have refined your selected plots for good titling, axis labels (with
units), and good aesthetic choices (e.g. color, transparency). After each plot,
make sure you justify why you chose each plot by describing what it shows.

### Plot One
```{r echo=FALSE, Plot_One}

```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}

```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}

```

### Description Three

------

# Reflection

> **Tip**: Here's the final step! Reflect on the exploration you performed and
the insights you found. What were some of the struggles that you went through?
What went well? What was surprising? Make sure you include an insight into
future work that could be done with the dataset.

> **Tip**: Don't forget to remove this, and the other **Tip** sections before
saving your final work and knitting the final report!